SIG Proceedings Paper in LaTeX Format

### 2017-05-22 samplebody-conf.tex
Add tables

We also experimented on customizing the way we input the features underneath our aforementioned networks. Instead of concatenating all feature into one vector, we tried to give weight for every feature we have. We argue that each feature have different contribution to the model. In order to do so, we create a new layer underneath our model to do the weighting scenario. The following equation to weight all feature can be seen in below:
\begin{equation}
	Z =  tanh(W _{1}*F_{1} + W_{2}*F_{2} + .. + W_{n}*F_{n})
\end{equation}
Where $W_{i}$ are the weight for each feature and $F_{i}$ are the extracted feature in vector form.
\section{EXPERIMENTS}
We mainly evaluated and analyzed our system on 416 manually annotated Indonesian medical questions.
\subsubsection{FEATURE ABLATION STUDY}
In this part, perform a feature ablation study. By considering all the features, and then removing one of these features, we want to estimate the importance of the features. To the experiment. We use 80\% as training set, and 20\% as a testing set. We used precision (P), recall (R), and F1-score (F1) as evaluation metrics. Table X show the experimental result. Then, we use LSTM as evaluation model because it is the most simple architecture. These are the following features we proposed: word stickiness (Ws), word abbreviation and acronym (Wa), Medical Entities (Me), Word Location (Wp), Word Length (Wl), Word Importance (Wi), POS tag (Pt), Medical Dictionary (Md).

\begin{table*}
	\caption{Feature Ablation Study Result}
	\label{tab:ablation}
	\begin{tabular}{cccl}
		\toprule
		Features&Precision&Recall&F-Measure\\
		\midrule
		Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & 1 in 1,000& For Swedish names&hehe\\
		$\pi$ & 1 in 5& Common in math&hehe\\
		\$ & 4 in 5 & Used in business&hehe\\
		$\Psi^2_1$ & 1 in 40,000& Unexplained usage&hehe\\
		\bottomrule
	\end{tabular}
\end{table*}

The experimental results in Table X shows that every feature has a positive contribution to the model. It is shown by iteratively remove each feature one by one and every time we remove a feature, F-1 score dropped. Hence, we use every feature to train our model in the next experiments.
Table X shows the performances of different methods.
\section{INI CONTOH}
\subsection{Type Changes and {\itshape Special} Characters}

>>>>

We also experimented on customizing the way we input the features underneath our aforementioned networks. Instead of concatenating all feature into one vector, we tried to give weight for every feature we have. We argue that each feature have different contribution to the model. In order to do so, we create a new layer underneath our model to do the weighting scenario. The following equation to weight all feature can be seen in below:
\begin{equation}
	Z =  tanh(W _{1}*F_{1} + W_{2}*F_{2} + .. + W_{n}*F_{n})
\end{equation}
Where $W_{i}$ are the weight for each feature and $F_{i}$ are the extracted feature in vector form.
\section{EXPERIMENTS}
In this section, we analyzed the importance of our features by conducting a feature ablation study. Furthermore, we also established a scenario to test the performance of our model.
\subsection{Feature Ablation Study}
In this part, perform a feature ablation study. By considering all the features, and then removing one of these features, we want to estimate the importance of the features. To the experiment. We use 80\% as training set, and 20\% as a testing set. We used precision (P), recall (R), and F1-score (F1) as evaluation metrics. Table \ref{tab:ablation} show the experimental result. Then, we use LSTM as evaluation model because it is the most simple architecture. These are the following features we proposed: word stickiness (Ws), word abbreviation and acronym (Wa), Medical Entities (Me), Word Location (Wp), Word Length (Wl), Word Importance (Wi), POS tag (Pt), Medical Dictionary (Md).

\begin{table*}
	\caption{Feature Ablation Study Result}
	\label{tab:ablation}
	\begin{tabular}{lccc}
		\toprule
		Features&Precision&Recall&F-Measure\\
		\midrule
			We + Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & 79.93\% & 57.45\% & 66.85\% \\

			Ws + Wa + Me + Wp + Wl + Wi + Pt + Md & 84.01\% & 75.79\% & 79.69\% \\

			We + Wa + Me + Wp + Wl + Wi + Pt + Md & 76.39\% & 73.59\% & 74.96\% \\

			We + Ws + Me + Wp + Wl + Wi + Pt + Md & 78.44\% & 73.83\% & 76.07\% \\

			We + Ws + Wa + Wp + Wl + Wi + Pt + Md & 79.38\% & 76.28\% & 77.8\% \\

			We + Ws + Wa + Me + Wl + Wi + Pt + Md & 74.24\% & 78.23\% & 76.19\% \\

			We + Ws + Wa + Me + Wp + Wi + Pt + Md & 75.36\% & 76.28\% & 75.82\% \\

			We + Ws + Wa + Me + Wp + Wl + Pt + Md & 83.69\% & 75.3\% & 79.27\% \\

			We + Ws + Wa + Me + Wp + Wl + Wi + Md & 79.68\% & 74.81\% & 77.17\% \\

			We + Ws + Wa + Me + Wp + Wl + Wi + Pt & 75.66\% & 76.03\% & 75.85\% \\
		\bottomrule
	\end{tabular}
\end{table*}

The experimental results in Table \ref{tab:ablation} shows that every feature has a positive contribution to the model. It is shown by iteratively remove each feature one by one and every time we remove a feature, F-1 score always dropped. Hence, we use every feature to train our model in the next experiments.
\subsection{Model Scenario}
We created a scenario to evaluate the performance of our model. In this scenario, we also compared our model to an unsupervised learning algorithm using RAKE. Moreover, we also implemented CRF to as a baseline for this sequence labeling task. CRF also has been proven effective in extracting keyphrases \cite{cao2010automatically} \cite{zhang2008automatic}. The following scenarios are listed below:
\begin{itemize}
	\item RAKE
	\item CRF
	\item B-LSTM
	\item CNN-B-LSTM
	\item Weighting-CNN-B-LSTM
\end{itemize}
The result of the scenario can be seen in Table \ref{tab:model_scenario}.
\begin{table}
	\caption{Model Scenario Result}
	\label{tab:model_scenario}
	\begin{tabular}{lccc}
		\toprule
		Models&Precision&Recall&F-Measure\\
		\midrule
			RAKE & 43.24\% & 68.19\% & 52.90\% \\

			CRF & 63.44\% & 64.94\% & 62.52\% \\

			LSTM & 78.77\% & 79.71\% & 79.16\% \\

			B-LSTM & 81.88\% & 83.05\% & 82.37\% \\

			CNN-B-LSTM & 82.00\% & 82.99\% & 82.41\% \\

		\bottomrule
	\end{tabular}
\end{table}
\section{INI CONTOH}
\subsection{Type Changes and {\itshape Special} Characters}
